### 2011-06-07 thesis/novelty-intro.tex
Related work on novelty detection.

The ability to identify novel cases is crucial in any autonomous system
that is deployed to unknown or to uncontrolled environments, as it gives the
system the ability to detect something is not conforming to it knowledge and
therefore should proceed with caution.
It has several applications such as fault detection, intrusion detection,
detection of masses in mammograms, hand written digit recognition and many
others.
% TODO: list usage of novelty detection together with references to papers
% with them.

@@

\subsection{Related Work}
\cite{ranganathan2010pliss} presents a system able to perform place recognition
and classification from visual clues. It is able to perform segmentation by
exploiting time-coherency on video information. The approach is particularly
interesting by its ability of keeping a fully probabilistic distribution of
the place classification and segmentation. This is, the system never performs
a deterministic decision that impacts any future , allowing it to adjust all
the segmentations and place classification as more data becomes available.
The system is also able to detect novel instances and methods how to adapt it
to run on a constant amount of memory and computation are presented.

@@

>>>>

The ability to identify novel cases is crucial in any autonomous system
that is deployed to unknown or to uncontrolled environments, as it gives the
system the ability to detect something is not conforming to it knowledge and
therefore should proceed with caution.
It has several applications such as fault detection~\cite{tarassenko1999novelty},
intrusion detection~\cite{fan2001using},
detection of masses in mammograms~\cite{tarassenko1995novelty}.
Any normal classification application is also a good candidate for extending
with novelty detection, as it allows to detect samples the system has not been
trained on and therefore the classification is considered
instable~\cite{devarakota2008reliability}.
E.g.\ applied to digit-recognition~\cite{tax1998outlier}
or to detection of novel inputs on a neural network~\cite{bishop1994novelty}.

@@

\subsection{Related Work}
\cite{zhang2005probabilistic} present a probabilistic semantic approach to image
annotation and retrieval with a multi-modal information. They introduce an
hidden variable modelling a concept present on a scene that connects together
information coming from both a bag of words and visual features extracted. By
training that hidden-variable their system becomes aware of possible existent
semantic categories and their relation between both textual and visual features.
Although not able to perform novelty detection, their approach is interesting by
the use of an hidden variable to probabilistic model the multi-modal sensors.

@@

\cite{ranganathan2010pliss} presents a system able to perform place recognition
and classification from visual clues. It is able to perform segmentation by
exploiting time-coherency on video information. The approach is particularly
interesting by its ability of keeping a fully probabilistic distribution of
the place classification and segmentation. This is, the system never performs
a deterministic decision that impacts any future result, allowing it to adjust
the segmentation and place classification as more data becomes available.
The system is also able to detect novel instances and methods how to adapt it
to run on a constant amount of memory and computation are presented.
